### 2021-10-03 paper/output/document/paper41.tex
writing on three flags

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Novel Formalization of the Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I present a custom formalization of the categorical imperative, as inspired by 
the goals from the previous chapter.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Logical Background%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The previous attempts to model the categorical imperative in Chapter 2 partially failed due to 
lack of expressivity about the complexity of a maxim. Specifically, they treated actions as a single, 
monolithic unit of evaluation, whereas most Kantians consider the unit of evaluation for the FUL to the more
complex notion of a maxim. In this section, I will present some logical background necessarily to more fully 
capture the spirit of a maxim. I will begin by borrowing some machinery to handle ``subjects" who perform 
actions from Chapter 2.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{typedecl}\isamarkupfalse%
\ s\ %
\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence%
}\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{Recall that an open sentence maps a subject to a term to model substitution.%
}\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{I define a maxim as a circumstance, act, goal pair (C, A, G), read 
as ``In circumstances C, do act A for goal G."  A circumstance is represented as a set of worlds 
$t$ where that circumstance holds. A goal is a term because it can be true or false at a world if it 
is realized. An act is an open sentence because, once we substitute an agent in, an act can be true or 
false at a world if it is actually performed by that subject.%
}%
\begin{isamarkuptext}%
My definition of a maxim is inspired by Onora O'Neill's work on maxims, and I will defend my representation
below and consider an additional component that Patricia Kitcher \cite{whatisamaxim} argues for.

$\textbf{O'Niell's Original Schematic and The Role of Practical Judgement}$

O'Neill$\footnote{p. 37}$ \cite{actingonprinciple} presents what Kitcher calls the widely accepted view that a maxim is a circumstance, 
act, goal tuple as I represented above. She views a maxim as a particular, subjective instantiation of a 
practical principle, which people may choose to act on or live by. Like a practical principle, a maxim 
is a kind of action-guiding rule and thus naturally includes an action and the circumstances under which 
it should be performed, which are often referred to as ``morally relevant circumstances."

She also includes the notion of a maxim's purpose or end (which I call goal) because Kant includes this in many of his 
example maxims and because Kant argues that human activity, because it is guided by a rational will, 
is inherently purposive. People do not act randomly, but instead in the pursuit of ends which they 
deem valuable \cite{sources}$\footnote{where in sources is this discussed}$. This inclusion is also essential 
for the version of the universalizability test that I will implement, explained in Section ??, so is 
ultimately uncontroversial.

O'Niell's inclusion of circumstances, on the other hand, is interesting because it leaves open the question of what qualifies as a 
relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection" \cite{whatisamaxim}$\footnote{Kitcher
on p.217 cites Wood p. 102 \cite{kantsethicalthought} as offering an example of a false positive due to this objection.}$, 
under which maxims are arbitrarily specified to pass the FUL. For example, the maxim ``When my name is Lavanya Singh,
I will lie to get some easy money," is universalizable, but is clearly a false positive. One solution to 
this problem is to argue that the circumstance ``When my name is Lavanya Singh" is not relevant 
to the rest of the maxim. This solution requires some discussion of what qualifies as a relevant circumstance.

O'Niell seems to adopt some version of this view when she concedes that a maxim cannot include ALL 
the infinitely many circumstances in which the agent may perform the action$\footnote{p. 37}$. She argues that this is 
an artifact of the fact that maxims are closely related to practical principles. Like any practical rule, 
maxims require an exercise of judgement to determine in which circumstances they should be applied. 
This judgement, applied in both choosing to exercise the maxim and in the formulation of the maxim 
itself, is what determines what qualifies as a ``morally relevant circumstance."

The implication for my project is that the computer cannot perform all ethical activity alone. 
Human judgement or the exercise of practical reason is essential to both formulate kinds maxims and 
determine when the actual conditions of life coincide with the circumstances in which the maxim is relevant. 
The second concern is less relevant to my project because analyzing a formal representation of the FUL requires 
making the circumstances in a given scenario precise. The first concern, on the other hand, demonstrates 
the important fact that ethics as presented here is not a solely computational activity. A
human being must create a representation for the dilemma they wish to test, effectively translating 
a complex, real situation into a flat logical structure. Not only will some of the situation's complexity
inevitably be lost, the outcome of the test will determine greatly on how the human formulates the maxim
and whether or not this formulation does indeed include morally relevant circumstances. If the human puts 
garbage into the test, the test will surely return garbage out.

While this may appear to be a weakness of my system, I believe that it actually
allows my system to retain some of the human complexity that many philosophers agree cannot be automated away.\footnote{Powers \cite{powers} presents 
the determination of morally relevant circumstances as an obstacle to the automation of Kantian ethics.}
Ethics is a fundamentally human activity. As Korsgaard argues, the categorical imperative is a statement 
about the properties of rational wills, i.e. our human wills. If ethics is meant to guide human behavior, 
the role of the computer becomes clear as not a replacement for our will (which is the entire focal point 
of Kantian ethics), but instead as a tool to help guide our wills and help us reason more efficiently 
and more effectively. Just as calculators don't render mathematicians obsolete, computational ethics
does not render human judgement obsolete. Chapter 4 Section ??  will be devoted to a more complete discussion 
of this issue.

$\textbf{Motive}$

Kitcher \cite{whatisamaxim} begins with O'Niell's (C, A, G) view and expands it to include the motivation 
behind performing the maxim. This additional component is read 
as ``In circumstance C, I will do A in order to G because of M." where M may be ``duty" or ``self-love."
This captures Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
Given that, under the Kantian constituvist view, the categorical
imperative completely defines duty, Kitcher argues that the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I would will that I and everyone else simultaneously
will do A in order to G in circumstance C." In other words, the affirmative result of the FUL becomes 
the motivation for a moral action.

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Niell's formulation suffices for the universalizability test, but is not the general notion of a maxim.
Notice that in order to pass the maxim through the FUL, it suffices to know C, A and G. The FUL
derives the purpose that Kitcher bundles into the maxim, so automating the FUL does not require 
including some notion of a purpose. The ``input" to the FUL is the (C, A, G) pair. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motivation requires modelling the operation of practical reason itself, 
which it outside the scope of this project. My work focuses on the FUL test itself, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's where ``acting from duty" starts to matter.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{fun}\isamarkupfalse%
\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}A\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Korsgaard claims that ``To will an end, rather than just
wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim, then, 
is to set yourself to, in the relevant circumstances, be the cause of its goal by taking the means 
specified in the maxim. This coheres with 
Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by. At worlds 
where the circumstances do not hold, a maxim is vacuously willed. If you decide to act on the rule ``I will 
do X in these cirumstances", then you are vacuously obeying it when the circumstances don't hold.

The above discussion implies that willing a maxim is particular to the agent, justifying my choice to 
require that a particular subject will a maxim. O'Niell argues for this interpretation when she distinguishes 
between the evaluation of a principle, which is generic, and a maxim, which she views as ``individuated only 
by referring to a person"$\footnote{p. 13}$ \cite{actingonprinciple}. I adopt the spirit of this interpretation but modify it slightly 
by representing the general maxim as a principle that anyone could adopt, and the act of willing the maxim 
as a person-particular instantiation of the maxim.

@@

If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper41.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%46=11%:%
%:%58=13%:%
%:%59=14%:%
%:%60=15%:%
%:%61=16%:%
%:%62=17%:%
%:%63=18%:%
%:%65=20%:%
%:%66=20%:%
%:%67=20%:%
%:%68=20%:%
%:%69=21%:%
%:%70=21%:%
%:%71=21%:%
%:%72=21%:%
%:%73=22%:%
%:%74=23%:%
%:%75=23%:%
%:%76=23%:%
%:%77=24%:%
%:%78=25%:%
%:%79=26%:%
%:%80=27%:%
%:%83=29%:%
%:%84=30%:%
%:%85=31%:%
%:%86=32%:%
%:%87=33%:%
%:%88=34%:%
%:%89=35%:%
%:%90=36%:%
%:%91=37%:%
%:%92=38%:%
%:%93=39%:%
%:%94=40%:%
%:%95=41%:%
%:%96=42%:%
%:%97=43%:%
%:%98=44%:%
%:%99=45%:%
%:%100=46%:%
%:%101=47%:%
%:%102=48%:%
%:%103=49%:%
%:%104=50%:%
%:%105=51%:%
%:%106=52%:%
%:%107=53%:%
%:%108=54%:%
%:%109=55%:%
%:%110=56%:%
%:%111=57%:%
%:%112=58%:%
%:%113=59%:%
%:%114=60%:%
%:%115=61%:%
%:%116=62%:%
%:%117=63%:%
%:%118=64%:%
%:%119=65%:%
%:%120=66%:%
%:%121=67%:%
%:%122=68%:%
%:%123=69%:%
%:%124=70%:%
%:%125=71%:%
%:%126=72%:%
%:%127=73%:%
%:%128=74%:%
%:%129=75%:%
%:%130=76%:%
%:%131=77%:%
%:%132=78%:%
%:%133=79%:%
%:%134=80%:%
%:%135=81%:%
%:%136=82%:%
%:%137=83%:%
%:%138=84%:%
%:%139=85%:%
%:%140=86%:%
%:%141=87%:%
%:%142=88%:%
%:%143=89%:%
%:%144=90%:%
%:%145=91%:%
%:%146=92%:%
%:%147=93%:%
%:%148=94%:%
%:%149=95%:%
%:%150=96%:%
%:%151=97%:%
%:%152=98%:%
%:%153=99%:%
%:%154=100%:%
%:%155=101%:%
%:%156=102%:%
%:%157=103%:%
%:%158=104%:%
%:%159=105%:%
%:%160=106%:%
%:%161=107%:%
%:%162=108%:%
%:%164=110%:%
%:%165=110%:%
%:%166=111%:%
%:%168=113%:%
%:%169=114%:%
%:%170=115%:%
%:%171=116%:%
%:%172=117%:%
%:%173=118%:%
%:%174=119%:%
%:%175=120%:%
%:%176=121%:%
%:%177=122%:%
%:%178=123%:%
%:%179=124%:%
%:%180=125%:%
%:%181=126%:%
%:%182=127%:%
%:%183=128%:%
%:%184=129%:%
%:%185=130%:%
%:%186=131%:%
%:%187=132%:%
%:%188=133%:%
%:%189=134%:%
%:%190=135%:%
%:%191=136%:%
%:%192=137%:%
%:%193=138%:%
%:%194=139%:%
%:%195=140%:%
%:%196=141%:%
%:%197=142%:%
%:%198=143%:%
%:%199=144%:%
%:%200=145%:%
%:%201=146%:%
%:%202=147%:%
%:%203=148%:%
%:%204=149%:%
%:%205=150%:%
%:%206=151%:%
%:%207=152%:%
%:%208=153%:%
%:%209=154%:%
%:%211=157%:%
%:%212=157%:%
%:%213=158%:%
%:%215=160%:%
%:%216=161%:%
%:%217=162%:%
%:%218=163%:%
%:%219=164%:%
%:%220=165%:%
%:%221=166%:%
%:%222=167%:%
%:%223=168%:%
%:%224=169%:%
%:%225=170%:%
%:%226=171%:%
%:%227=172%:%
%:%228=173%:%
%:%229=174%:%
%:%230=175%:%
%:%231=176%:%
%:%232=177%:%
%:%233=178%:%
%:%234=179%:%
%:%235=180%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{4}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Novel Formalization of the Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I present a custom formalization of the categorical imperative, as inspired by 
the goals from the previous chapter.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Logical Background%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The previous attempts to model the categorical imperative in Chapter 2 partially failed due to 
lack of expressivity about the complexity of a maxim. Specifically, they treated actions as a single, 
monolithic unit of evaluation, whereas most Kantians consider the unit of evaluation for the FUL to the more
complex notion of a maxim. In this section, I will present some logical background necessarily to more fully 
capture the spirit of a maxim. I will begin by borrowing some machinery to handle ``subjects" who perform 
actions from Chapter 2.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{typedecl}\isamarkupfalse%
\ s\ %
\isamarkupcmt{s is the type for a ``subject," i.e. the subject of a sentence%
}\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ os\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}s\ {\isasymRightarrow}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{Recall that an open sentence maps a subject to a term to model substitution.%
}\isanewline
\isanewline
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\ %
\isamarkupcmt{I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
as ``In circumstances C, act A for goal G." Isabelle's strict typing rules mean that the choice of the 
type of each member of this tuple is significant. A circumstance is represented as a set of worlds 
$t$ where that circumstance holds. A goal is also a term because it can be true or false at a world if it 
is realized or not. An act is an open sentence because an act itself is not the kind of thing that can 
be true or false (as in, an act is not truth-apt), but the combination of a subject performing an act 
can be true or false at a world depending on whether or not the act is indeed performed by that subject. 
For example, ``running" is not truth-apt, but ``Sara runs" is truth-apt.%
}%
\begin{isamarkuptext}%
I define a maxim as a circumstance, act, goal tuple (C, A, G), read 
as ``In circumstances C, act A for goal G." Isabelle's strict typing rules mean that the choice of the 
type of each member of this tuple is significant. A circumstance is represented as a set of worlds 
$t$ where that circumstance holds. A goal is also a term because it can be true or false at a world if it 
is realized or not. An act is an open sentence because an act itself is not the kind of thing that can 
be true or false (as in, an act is not truth-apt), but the combination of a subject performing an act 
can be true or false at a world depending on whether or not the act is indeed performed by that subject. 
For example, ``running" is not truth-apt, but ``Sara runs" is truth-apt.

My definition of a maxim is inspired by Onora O'Neill's work on maxims. I will defend my representation
below and consider an additional component that Patricia Kitcher argues for.

$\emph{O'Niell's Original Schematic and The Role of Practical Judgement}$

O'Neill$\footnote{p. 37}$ \cite{actingonprinciple} presents what Kitcher \cite{whatisamaxim}  calls the widely accepted 
view that a maxim is a circumstance, act, goal tuple. A maxim 
is an action-guiding rule and thus naturally includes an act and the circumstances under which 
it should be performed, which are often referred to as ``morally relevant circumstances."

She also includes a purpose, end, or goal in the maxim because Kant includes this in many of his 
example maxims and because Kant argues that human activity, because it is guided by a rational will, 
is inherently purposive\cite{groundwork}\footnote{(G 4:428)}. A rational will does not act randomly (else it would not be rational), 
but instead in the pursuit of ends which it deems valuable. This inclusion is also essential for the version of the universalizability test 
that I will implement, explained in Section ??.

O'Neill's inclusion of circumstances is potentially controversial because it leaves open the question of what qualifies as a 
relevant circumstance for a particular maxim. This is gives rise to ``the tailoring objection" \cite{whatisamaxim}$\footnote{Kitcher
on p.217 cites Wood p. 102 \cite{kantsethicalthought} as offering an example of a false positive due to this objection.}$, 
under which maxims are arbitrarily specified to pass the FUL. For example, the maxim ``When my name is Lavanya Singh,
I will lie to get some easy money," is universalizable, but is clearly a false positive. One solution to 
this problem is to argue that the circumstance ``When my name is Lavanya Singh" is not morally relevant 
to the act and goal. This solution requires some discussion of what qualifies as a relevant circumstance.

O'Neill seems to acknowledge the difficult of determining relevant circumstances when she concedes that a maxim cannot include all 
of the infinitely many circumstances in which the agent may perform the action$\footnote{p. 37}$. She argues that this is 
an artifact of the fact that maxims are rules of practical reason, the kind of reason that helps us decide what to do 
and how to do it \cite{bok}. Like any practical rule, 
maxims require the exercise of practical judgement to determine in which circumstances they should be applied. 
This judgement, applied in both choosing when to exercise the maxim and in the formulation of the maxim 
itself, is what determines the ``morally relevant circumstances."

The upshot for computational ethics is that the computer cannot perform all ethical activity alone. 
Human judgement and the exercise of practical reason are essential to both formulate maxims and 
determine when the actual conditions of life coincide with the circumstances in which the maxim is relevant. 
Choosing when to exercise a maxim is less relevant to my project because analyzing a formal representation of the FUL requires 
making the circumstances in a given scenario precise, but will be important for applications of 
computational ethics to guiding AI agents. The difficulty in formulating a maxim, on the other hand, demonstrates 
the important fact that ethics, as presented here, is not a solely computational activity. A
human being must create a representation for the dilemma they wish to test, effectively translating 
a complex, real situation into a flat logical structure. This parallels the challenge that programmers 
face when translating the complexity of reality to a programming langauge or computational representation. Not only will some of the situation's complexity
inevitably be lost, the outcome of the universalizability test will depend on how the human formulates the maxim
and whether or not this formulation does indeed include morally relevant circumstances. If the human puts 
garbage into the test, the test will return garbage out.

While this may appear to be a weakness of my system, I believe that it actually
allows my system to retain some of the human complexity that many philosophers agree cannot be automated away.\footnote{Powers \cite{powers} presents 
the determination of morally relevant circumstances as an obstacle to the automation of Kantian ethics.}
Ethics is a fundamentally human activity. Kant argues that the categorical imperative is a statement 
about the properties of rational wills. In fact, Korsgaard argues that morality derives its authority over us, 
or normativity, only because is it a property of a rational will, and we, as human beings, are rational wills.
If ethics is meant to guide human behavior, the role of the computer becomes clear as not a replacement for our will,
but instead as a tool to help guide our wills and reason more efficiently 
and more effectively. Just as calculators don't render mathematicians obsolete, computational ethics
does not render human judgement or philosophy obsolete. Chapter 4 Section ?? will be devoted to a more complete discussion 
of this issue.

$\emph{Exclusion of Motive}$

Kitcher \cite{whatisamaxim} begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
behind performing the maxim. This additional component is read 
as ``In circumstance C, I will do A in order to G because of M," where M may be ``duty" or ``self-love."
Kitcher argues that the inclusion of motive is necessary for the fullest, most general form of a maxim
in order to capture Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
Under this view, the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
will do A in order to G in circumstance C." In other words, if Kant is correct in arguing that moral 
actions must be done from the motive of duty, the affirmative result of the FUL becomes 
the motive for a moral action.

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal pair. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{fun}\isamarkupfalse%
\ will\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}maxim\ {\isasymRightarrow}\ s{\isasymRightarrow}\ \ t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}A\ {\isacharunderscore}\ {\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}will\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s\ {\isacharequal}\ {\isacharparenleft}c\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}a\ s{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Korsgaard claims that ``to will an end, rather than just
wishing for it or wanting it, is to set yourself to be its cause" \cite{sources}. To will a maxim, then, 
is to set yourself to, in the relevant circumstances, be the cause of its goal by taking the means 
specified in the maxim. This coheres with 
Kitcher's and Korsgaard's understanding of a maxim as a principle or rule to live by. At worlds 
where the circumstances do not hold, a maxim is vacuously willed. If you decide to act on the rule ``I will 
do X in these cirumstances", then you are vacuously obeying it when the circumstances don't hold.

The above discussion implies that willing a maxim is particular to the agent, justifying my choice to 
require that a particular subject will a maxim. O'Neill argues for this interpretation when she distinguishes 
between the evaluation of a principle, which is generic, and a maxim, which she views as ``individuated only 
by referring to a person"$\footnote{p. 13}$ \cite{actingonprinciple}. I adopt the spirit of this interpretation but modify it slightly 
by representing the general maxim as a principle that anyone could adopt, and the act of willing the maxim 
as a person-particular instantiation of the maxim.

@@

If the circumstances do not hold and the goal is achieved, then the maxim is vacuously effective, since 
it is vacuously willed (as described above). While this scenario is counterintuitive, it is not very 
interesting for my purposes because, when the circumstances do not hold, a maxim is not applicable. It 
doesn't really make sense to evaluate a maxim when it's not supposed to be applied. The maxim ``When on Jupiter,
read a book to one-up your nemesis" is vacuously effective because it can never be disproven.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/paper41.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%46=11%:%
%:%58=13%:%
%:%59=14%:%
%:%60=15%:%
%:%61=16%:%
%:%62=17%:%
%:%63=18%:%
%:%65=20%:%
%:%66=20%:%
%:%67=20%:%
%:%68=20%:%
%:%69=21%:%
%:%70=21%:%
%:%71=21%:%
%:%72=21%:%
%:%73=22%:%
%:%74=23%:%
%:%75=23%:%
%:%76=23%:%
%:%77=24%:%
%:%78=25%:%
%:%79=26%:%
%:%80=27%:%
%:%81=28%:%
%:%82=29%:%
%:%83=30%:%
%:%86=32%:%
%:%87=33%:%
%:%88=34%:%
%:%89=35%:%
%:%90=36%:%
%:%91=37%:%
%:%92=38%:%
%:%93=39%:%
%:%94=40%:%
%:%95=41%:%
%:%96=42%:%
%:%97=43%:%
%:%98=44%:%
%:%99=45%:%
%:%100=46%:%
%:%101=47%:%
%:%102=48%:%
%:%103=49%:%
%:%104=50%:%
%:%105=51%:%
%:%106=52%:%
%:%107=53%:%
%:%108=54%:%
%:%109=55%:%
%:%110=56%:%
%:%111=57%:%
%:%112=58%:%
%:%113=59%:%
%:%114=60%:%
%:%115=61%:%
%:%116=62%:%
%:%117=63%:%
%:%118=64%:%
%:%119=65%:%
%:%120=66%:%
%:%121=67%:%
%:%122=68%:%
%:%123=69%:%
%:%124=70%:%
%:%125=71%:%
%:%126=72%:%
%:%127=73%:%
%:%128=74%:%
%:%129=75%:%
%:%130=76%:%
%:%131=77%:%
%:%132=78%:%
%:%133=79%:%
%:%134=80%:%
%:%135=81%:%
%:%136=82%:%
%:%137=83%:%
%:%138=84%:%
%:%139=85%:%
%:%140=86%:%
%:%141=87%:%
%:%142=88%:%
%:%143=89%:%
%:%144=90%:%
%:%145=91%:%
%:%146=92%:%
%:%147=93%:%
%:%148=94%:%
%:%149=95%:%
%:%150=96%:%
%:%151=97%:%
%:%152=98%:%
%:%153=99%:%
%:%154=100%:%
%:%155=101%:%
%:%156=102%:%
%:%157=103%:%
%:%158=104%:%
%:%159=105%:%
%:%160=106%:%
%:%161=107%:%
%:%162=108%:%
%:%163=109%:%
%:%164=110%:%
%:%165=111%:%
%:%166=112%:%
%:%167=113%:%
%:%168=114%:%
%:%169=115%:%
%:%170=116%:%
%:%171=117%:%
%:%172=118%:%
%:%173=119%:%
%:%174=120%:%
%:%175=121%:%
%:%176=122%:%
%:%177=123%:%
%:%179=125%:%
%:%180=125%:%
%:%181=126%:%
%:%183=128%:%
%:%184=129%:%
%:%185=130%:%
%:%186=131%:%
%:%187=132%:%
%:%188=133%:%
%:%189=134%:%
%:%190=135%:%
%:%191=136%:%
%:%192=137%:%
%:%193=138%:%
%:%194=139%:%
%:%195=140%:%
%:%196=141%:%
%:%197=142%:%
%:%198=143%:%
%:%199=144%:%
%:%200=145%:%
%:%201=146%:%
%:%202=147%:%
%:%203=148%:%
%:%204=149%:%
%:%205=150%:%
%:%206=151%:%
%:%207=152%:%
%:%208=153%:%
%:%209=154%:%
%:%210=155%:%
%:%211=156%:%
%:%212=157%:%
%:%213=158%:%
%:%214=159%:%
%:%215=160%:%
%:%216=161%:%
%:%217=162%:%
%:%218=163%:%
%:%219=164%:%
%:%220=165%:%
%:%221=166%:%
%:%222=167%:%
%:%223=168%:%
%:%224=169%:%
%:%226=172%:%
%:%227=172%:%
%:%228=173%:%
%:%230=175%:%
%:%231=176%:%
%:%232=177%:%
%:%233=178%:%
%:%234=179%:%
%:%235=180%:%
%:%236=181%:%
%:%237=182%:%
%:%238=183%:%
%:%239=184%:%
%:%240=185%:%
%:%241=186%:%
%:%242=187%:%
%:%243=188%:%
%:%244=189%:%
%:%245=190%:%
%:%246=191%:%
%:%247=192%:%
%:%248=193%:%
%:%249=194%:%
%:%250=195%:%
